Paper Analysis

### 2025-04-18 Paper_WriteUp/Paper_Plots.qmd
moving unnecessary plots to appendix section

```{r}
#| eval: false
## TO DO - move to supplement
## not required for a paper plot
player_pars_pre <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

## Bullet vs Blitz for 17-19

@@

```{r bullet v blitz for 17-19}
#| eval: false

@@

```{r}
#| eval: false
## player effects also
comp_gm_player <- player_pars_bullet |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")

@@

>>>>

@@

@@

@@

### OTHER

## Bullet vs Blitz for 17-19
```{r bullet v blitz for 17-19}
#| eval: false

#winner and player effects for bullet vs blitz
```{r}
#| eval: false
## TO DO - move to supplement
## not required for a paper plot
player_pars_pre <- fit_gm_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id") |> 
  mutate(model = "Prev. Game")

#bullet vs blitz player effects for GMs
```{r}
#| eval: false
## player effects also
comp_gm_player <- player_pars_bullet |> 
  filter(param == 1) |> 
  mutate(y = reorder(player_name, value, FUN = median)) |> 
  bind_rows(player_pars_blitz |> 
              filter(param == 1) |> 
              mutate(y = as.factor(player_name))) |> 
  ggplot(aes(x = value, y = y,
             color = model)) +
  stat_pointinterval(position = ggstance::position_dodgev(height = 0.5)) +
  labs(x = element_blank(), y = element_blank(), color = element_blank()) +
  theme_single_y() +
  theme(legend.position = "bottom") +
  scale_x_continuous(breaks = breaks_pretty(n = 3)) +
  scale_color_viridis_d(option = "H")
